Open Data Quality Is Poor but Slowly Improving

### 2021-01-30 outputs/paper/paper.Rmd
fix gridlines

  # Correctly format the dates for easy readability:
  scale_x_datetime(limits = as.POSIXct(strptime(c("2019-12-16 10:00:00", "2021-01-25 10:00:00"), 
                                                 format = "%Y-%m-%d %H:%M:%S")),
                   expand = c(0, 0),  # keep the sides of the plot snug to the limits
                   labels = date_format("%b\n%Y"),  # Format the x-axis scale to show month names
                   breaks = c(as.POSIXct("2020-01-01 01:00:00"),  # Set breaks on the first of the month
                              as.POSIXct("2020-03-01 01:00:00"),
                              as.POSIXct("2020-05-01 01:00:00"),
                              as.POSIXct("2020-07-01 01:00:00"),
                              as.POSIXct("2020-09-01 01:00:00"),
                              as.POSIXct("2020-11-01 01:00:00"),
                              as.POSIXct("2021-01-01 01:00:00")),
                    minor_breaks = NULL,  # Remove minor break lines
                   ) +

@@

  # Summarise counts and means for each month:
  summarise(scored = n_distinct(package),
            scores = n_distinct(date_scored),
            mean_accessibility = mean(accessibility),
            mean_completeness = mean(completeness),
            mean_freshness = mean(freshness),
            mean_metadata = mean(metadata),
            mean_usability = mean(usability),
            mean_quality = mean(quality)
  ) %>%
  # Tidy up names so they are better for the table display:
  rename("Unique Packages Scored" = scored,
         "Times the Portal was Scored" = scores, 
         "Accessibility" = mean_accessibility,
         "Completeness" = mean_completeness, 
         "Freshness" = mean_freshness, 
         "Metadata" = mean_metadata,
         "Usability" = mean_usability, 
         "Quality" = mean_quality) %>%
  mutate_if(is.numeric, round, 3) # round score averages to 3 decimal places

@@

  # Style the table:
  add_header_above(c("", "Manual Scoring" = 3, "Scheduled Scoring" = 7), align = "l") %>%
  column_spec(1, width = "14em") %>%
  column_spec(2, width = "3em") %>%
  column_spec(3, width = "3em") %>%
  column_spec(4, width = "3em") %>%
  column_spec(5, width = "3em") %>%
  column_spec(6, width = "3em") %>%
  column_spec(7, width = "3em") %>%
  column_spec(8, width = "3em") %>%
  column_spec(9, width = "3em") %>%
  column_spec(10, width = "3em") %>%
  column_spec(11, width = "3em") %>%
  pack_rows("Counts", 1, 2) %>%
  pack_rows("Average Scores", 3, 8) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
```

>>>>

  # Correctly format the dates for easy readability:
  scale_x_datetime(limits = as.POSIXct(strptime(c("2019-12-16 10:00:00", "2021-01-25 10:00:00"), 
                                                 format = "%Y-%m-%d %H:%M:%S")),
                   expand = c(0, 0),  # keep the sides of the plot snug to the limits
                   labels = date_format("%b\n%Y"),  # Format the x-axis scale to show month names
                   breaks = c(as.POSIXct("2020-01-01 01:00:00"),  # Set breaks on the first of the month
                              as.POSIXct("2020-03-01 01:00:00"),
                              as.POSIXct("2020-05-01 01:00:00"),
                              as.POSIXct("2020-07-01 01:00:00"),
                              as.POSIXct("2020-09-01 01:00:00"),
                              as.POSIXct("2020-11-01 01:00:00"),
                              as.POSIXct("2021-01-01 01:00:00")),
                    #minor_breaks = NULL,  # Remove minor break lines
                   ) +

@@

  # Summarise counts and means for each month:
  summarise(scored = n_distinct(package),
            scores = n_distinct(date_scored),
            mean_accessibility = mean(accessibility),
            mean_completeness = mean(completeness),
            mean_freshness = mean(freshness),
            mean_metadata = mean(metadata),
            mean_usability = mean(usability),
            mean_quality = mean(quality)
  ) %>%
  # Tidy up names so they are better for the table display:
  rename("Unique packages scored" = scored,
         "Times the portal was scored" = scores, 
         "Accessibility" = mean_accessibility,
         "Completeness" = mean_completeness, 
         "Freshness" = mean_freshness, 
         "Metadata" = mean_metadata,
         "Usability" = mean_usability, 
         "Quality" = mean_quality) %>%
  mutate_if(is.numeric, round, 3) # round score averages to 3 decimal places

@@

  # Style the table:
  add_header_above(c("", "Manual scoring" = 3, "Scheduled scoring" = 7), align = "l") %>%
  column_spec(1, width = "14em") %>%
  column_spec(2, width = "3em") %>%
  column_spec(3, width = "3em") %>%
  column_spec(4, width = "3em") %>%
  column_spec(5, width = "3em") %>%
  column_spec(6, width = "3em") %>%
  column_spec(7, width = "3em") %>%
  column_spec(8, width = "3em") %>%
  column_spec(9, width = "3em") %>%
  column_spec(10, width = "3em") %>%
  column_spec(11, width = "3em") %>%
  pack_rows("Counts", 1, 2) %>%
  pack_rows("Average Scores", 3, 8) %>%
  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
```
